---
title: "Design of Experiment"
format: html
editor: visual
---

#Load libraries

```{r}
library(tidyverse)
library(agricolae)
```

# Completely Randomized Design - CRD

```{r}
trt <- c("G1","G2","G3","G4","G5")
plan <- design.crd(trt,3, seed=7638)
plan <- plan$book
View(plan)
```

# Write out the plan
```{r}
write_csv(plan, file = "data/CRDplan.csv")

```

# Randomized Complete Block Design - RCBD

```{r}
trt1 <- c("A","B","C","D","E")
plan2 <- design.rcbd(trt1, 4, seed = 161)
plan2 <- plan2$book
View(plan2)
```

# write out the plan
```{r}
write_csv(plan2, file = "data/RCBDplan.csv")

```

# Split Plot Design
```{r}
phosphorus <- c('0 kg P','37.5 kg P','75 kg P')


varieties <- c('TME419','TMS581')


plan4 <- design.split(trt1 = phosphorus,trt2 = varieties,r = 4,seed = 123)

plan4 <- plan4$book

View(plan4)
```

# write out the plan
```{r}
write_csv(plan4, file = "data/SplitPlot.csv")

```

# Alpha Lattice Design

```{r}
trt <- 1:30 # Treatment
#trt <- letters[1:12] 
t <- length(trt)
# size block k
k <- 3 # Size of blocks
# Blocks s
s <- t/k # Number of blocks
# replications r
r <- 2  # replication

plan5 <- design.alpha(trt,k,r,serie=2, seed=1234)

plan5 <- plan5$book

View(plan5)
```

# write out the plan

```{r}
write_csv(plan5, file = "data/ADplan.csv")

```

# Latin Square Design

```{r}
varieties<-c("perricholi","yungay","maria bonita","tomasa")

outdesign <-design.lsd(varieties,serie=2,seed=23)

lsd <- outdesign$book
```


# write out the plan

```{r}
write_csv(lsd, file = "data/LSD.csv")

```

# Your Turn

- A researcher has seven (5) genotypes to be tested with 3 different levels of Potassium (No
treatment, 50%, and 100% of the recommendation). Choose a appropriate design and then design the experiment using R.

